A Kochen-Specker system has at least 21 vertices\\ {\small (extended abstract)}

### 2014-04-14 main.tex

With this method, we have decided in an hour the embeddability
of every squarefree graph with minimal vertex order three of 13
vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal 20
    contains as a subgraph one of
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    which are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a direct proof.

>>>>

With this method, we have decided in an hour the embeddability
of every squarefree graph with minimal vertex order three of 13
vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal to 20
    contains, as a subgraph, one of the following three graphs:
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    These three graphs are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a similar direct proof. The third graph is shown to not be embeddable using our algorithm.
